\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-03-21 paper/main.tex
pass on intro

\sloppy Serveral important application domains (e.g., transportation,
medicine, etc.) use AI as part of their business processes. Deep
Learning~(DL) libraries, such as \jax, \torch{}, and \tf{}, provide
the building blocks for the AI components of these applications.
Unfortunately, as any piece of software, these libraries contain
bugs. An impressive number of techniques have been recently proposed
to find bugs in these
libraries~\cite{wei2022free,xie2022docter,deng2022fuzzing,pham2019cradle,guo2020audee,wang2020deep,gu2022muffin,deng2023large,liu2023nnsmith,liu2023neuri,shi2023acetest,deng2023largeedge},
however we observe that the evaluation of these techniques do
\emph{not} use a reference set of reproducible bugs to evaluate their
effectiveness. The lack of evaluation standards is an obstacle to the
fair comparison of techniques, hindering research progress.
\Fix{Clarify how the "evaluation set" used by the existing works is different from the "reference set" that we are proposing. Also, need more compelling reason/some sort of evaluation of other fuzzers
to complement the motivation}

@@

We present \tname, a database of curated reproducible bugs to
enable credible evaluation of DL library testing techniques. \tname\ is
equipped with a command-line interface to enable researchers to analyze
and reproduce bug instances.

\tname\ has been under active development since March 21, 2024, the
day of the first commit in its GitHub repository. Two UROP students,
two PhD students, and two faculty were involved in the work during
this period. Details on tool availability is provided in
Section~\ref{sec:tool-availability}.

\Fix{Need to add text regarding differentiating the tool from BugsInPy}

>>>>

\sloppy Several application domains (e.g., transportation and
medicine) use AI as part of their solutions. Deep Learning~(DL)
libraries, such as \jax, \torch{}, and \tf{}, provide the building
blocks for the AI components of these applications.  Unfortunately, as
any piece of software, these libraries contain bugs. An impressive
number of techniques have been recently proposed to find bugs in these
libraries~\cite{wei2022free,xie2022docter,deng2022fuzzing,pham2019cradle,guo2020audee,wang2020deep,gu2022muffin,deng2023large,liu2023nnsmith,liu2023neuri,shi2023acetest,deng2023largeedge},
however we observe these techniques propose an independent evaluation
methodology. These techniques do \emph{not} use a reference database
of reproducible bugs to evaluate their effectiveness. The lack of an
evaluation standards is a serious obstacle to a fair and rigorous
comparison of techniques and hinders research progress.

%%~\cite{just2014defects4j,smytzek2024tests4py,widyasari2020bugsinpy,kim2021denchmark}
Although many datasets of reproducible bugs have been proposed in the
literature, there is a lack of solutions satisfying the following
criteria:

\begin{enumerate}[leftmargin=0.2in]
\item developers should be able to write tests scripts in Python;
\item ~they should be able to handle nighly builds and specific
  versions of CUDA (\textsection~\ref{sec:challenges});
\item they should be able to integrate fuzzing tools in the framework.
\end{enumerate}

Note that DL libraries are written in Python. Existing datasets of
reproducible bugs exist in Python (e.g.,
BugInPy~\cite{widyasari2020bugsinpy} and
Tests4Py~\cite{smytzek2024tests4py}), but they fail to satisfy the
second or the third requirement. For example, BugsInPy and Tests4Py do
not support artifacts in Docker, which are necessary to modify CUDA
drivers in the guest OS to reproduce specific GPU-related
bugs.\footnote{BugsInPy and Tests4Py use python virtual environments,
e.g., venv and pyenv.} More importantly, a dataset of Deep Learning
Libraries needs to support the integration of new fuzzing tools. The
central purpose of such dataset is to \emph{enable the systematic
evaluation of testing techniques}.

%% \Fix{Clarify how the
%%   "evaluation set" used by the existing works is different from the
%%   "reference set" that we are proposing. Also, need more compelling
%%   reason/some sort of evaluation of other fuzzers to complement the
%%   motivation}

@@

We present \tname, a database of curated reproducible bugs to enable
credible evaluation of DL library testing techniques. \tname\ is
equipped with a command-line interface to enable researchers to
analyze and reproduce bug instances.  \tname\ has been under active
development since March 21, 2024, the day of the first commit in its
GitHub repository. Two UROP students, two PhD students, and two
faculty were involved in the work during this
period. Section~\ref{sec:tool-availability} details tool availability.

%\Fix{Need to add text regarding differentiating the tool from BugsInPy}
